% LaTeX source of my resume
% =========================

% Commented for easy reuse... ;)

% See the `README.md` file for more info.

% This file is licensed under the CC-NC-ND Creative Commons license.

% Start a document with the here given default font size and paper size.
\documentclass[10pt,a4paper]{article}

% Set the page margins.
\usepackage[a4paper,margin=0.75in]{geometry}

% For spanish accents and the like
\usepackage[utf8]{inputenc}

% Setup the language.
\usepackage[english]{babel}
\hyphenation{Some-long-word}

% Makes resume-specific commands available.
\usepackage{resume}

\begin{document}  % begin the content of the document
\sloppy  % this to relax whitespacing in favour of straight margins


% title on top of the document
\maintitle{Julio C. Villasante G\'omez}{May 24, 1980}{Last update on \today}

\nobreakvspace{0.3em}  % add some page break averse vertical spacing

% \noindent prevents paragraph's first lines from indenting
% \mbox is used to obfuscate the email address
% \sbull is a spaced bullet
% \href well..
% \\ breaks the line into a new paragraph
\noindent\href{mailto:jvillasantegomez.at.gmail.dot.com}{jvillasantegomez\mbox{}@\mbox{}gmail.com}\sbull
\textsmaller{+}1-786-282-1636\sbull
\href{https://github.com/jvillasante}{github.com/jvillasante}\sbull
\href{http://linkedin.com/in/jvillasante}{linkedin.com/in/jvillasante}
\\
\makebox[\textwidth]{
  Bradenton,\thinspace Florida\sbull
  {\large \sc 34202}\sbull
  USA
}

\spacedhrule{0.9em}{-0.4em}  % a horizontal line with some vertical spacing before and after

\roottitle{Summary}  % a root section title

\vspace{-1.3em}  % some vertical spacing
\begin{multicols}{2}  % open a multicolumn environment
\noindent \emph{Savvy Software Developer with 10+ years in technical software development. Expert in a variety of platforms, languages and embedded systems.}
\\
\\
An excellent problem solver, able to quickly grasp complex systems and identify opportunities for improvements and resolution of critical issues.

Have interest in designing and crafting efficient modern software, and learning new technologies and tools if need arises.
\end{multicols}

\spacedhrule{0em}{-0.4em}

\roottitle{Experience}

\headedsection
  {\href{http://www.ascom.us/}{Ascom Wireless Solutions}}
  {\textsc{Florida, USA}} {%
  \headedsubsection
    {Software Engineer}
    {Feb \apo16 -- Present}
    {\bodytext{Research and development focusing on innovative and reliable technologies for call systems, medical device integration, and wireless telephony to support and optimize our customers' mission-critical processes.}}
    {\bodytext{
        \begin{itemize}
          \item Embedded development using \acr{C/C++} and \acr{QT} over Linux.
          \item Medical device communication through \acr{UDP} and \acr{AMQP}.
          \item Wrote features on all levels of the solution (OS, Data, Business Logic, UI)
          \item Taking care of big legacy code and trying to make it better.
        \end{itemize}

        \vspace{1mm}

        \textbf{Skillset:} Operating Systems (mostly \acr{LINUX}); \acr{QT}; Data Structures; Algorithms; Performance design and analysis; \acr{AMQP}; \acr{RabbitMQ}; Networking; \acr{SQLite} Databases.\\
        \textbf{Languages:} Primarily \acr{C} \& \acr{C++} in a UNIX-like environment; Shell Scripting.\\
    }}
}

\headedsection
  {\href{https://www.privicee.com/}{Privicee}}
  {\textsc{Florida, USA}} {%
  \headedsubsection
    {Software Developer}
    {Aug \apo15 -- Jan \apo16}
    {\bodytext{Startup focusing on The Internet with the end user in mind. They are introducing disruptive business model into niche markets and building quality products that create elegant solutions for changing the way internet experiences are delivered.}}
    {\bodytext{
        \begin{itemize}
          \item Wrote cross platform \acr{C} daemon to manage all states of internet connection and \acr{VPN}.
          \item Wrote both \acr{Unix/Linux} and \acr{Mac} clients that communicate with \acr{C} daemon using \acr{IPC}.
          \item Wrote a \acr{REST} API to manage a \acr{VPN} server remotely.
          \item Wrote \acr{REST} APIs for murmur server, discourse and other third party solutions that we used.
          \item Wrote complete \acr{Dropbox} clone backend.
          \item Resolved some scalability issues by using message queues.
        \end{itemize}

        \vspace{1mm}

        \textbf{Skillset:} Operating Systems; Data Structures; Algorithms; Performance design and analysis; \acr{VPN} Networks; Networking; \acr{NoSQL} Databases (\acr{MongoDB}); \acr{Redis}.\\
        \textbf{Languages:} Primarily \acr{C} \& \acr{C++} in a UNIX-like environment; Shell Scripting; \acr{Objective-C/Swift}; \acr{JavaScript} (\acr{Node.js}).\\
    }}
}

\headedsection
  {\href{http://innobis.cl}{Innobis}}
  {\textsc{Santiago, Chile}} {%
  \headedsubsection
    {Lead Developer}
    {Jan \apo15 -- June \apo15}
    {\bodytext{
        \begin{itemize}
          \item Drafted and carried out the vision for my department: got everyone to look beyond PHP to other
            open source solutions such as \acr{Node.js} \& \acr{React.js/Flux}.
          \item Wrote complete backend and frontend for a new project using sound new technologies with time
            constraints: Made the company meet their clients on time.
        \end{itemize}

        \vspace{1mm}

        \textbf{Skillset:} Architecture \& Design; Relational Databases (\acr{PostgreSQL}); Server-side
        \acr{JavaScript} (\acr{Node.js}); Client-side \acr{JavaScript} with \acr{React.js} \& \acr{Flux};
        \acr{HTML5}; \acr{CSS}.\\
        \textbf{Languages:} \acr{Javascript}; Shell Scripting; \acr{PL/pgSQL}.\\
    }}
}

\headedsection
  {\href{http://www.genera.cl}{Genera S.A.}}
  {\textsc{Santiago, Chile}} {%
  \headedsubsection
    {Lead Developer}
    {Jan \apo14 -- Jan \apo15}
    {\bodytext{
        \begin{itemize}
        \item Lead the Research \& Development department reporting directly to the general director.
        \item Wrote biometric solutions using heavy \acr{C++} and \acr{QT} that ran on \acr{ARM} boards.
        \item Wrote code to interact with third party hardware: sensors, keypads, etc.
        \item Wrote \acr{C++} libraries that we were able to reuse on most of our projects.
        \item Reduced time on biometric fingerprint identification by writing more performant algorithms and
          data structures.
        \end{itemize}

        \vspace{1mm}

        \textbf{Skillset:} Operating Systems; Data Structures; Algorithms; Performance design and analysis;
        Concurrency; Biometrics; Networking; \acr{QT}; \acr{ARM}; Embedded Linux.\\
        \textbf{Languages:} Primarily \acr{C} \& \acr{C++} in a UNIX-like environment; Shell Scripting; \acr{SQL}.\\
    }}
}

\headedsection
  {\href{http://www.datys.cu}{Datys}}
  {\textsc{Havana, Cuba}} {%
  \headedsubsection
    {Lead Developer}
    {\apo09 -- Jan \apo14}
    {\bodytext{
        \begin{itemize}
        \item Lead the development of a \acr{POS} system for our clients.
        \item Contributed with other teams on different projects ranging from biometrics to internal tools
          development.
        \item Got involved with the software architecture, design and development of all technically
          challenging projects I could get my hands on.
        \end{itemize}

        \vspace{1mm}

        \textbf{Skillset:} Operating Systems; Data Structures; Algorithms; Performance design and analysis;
        Biometrics; Networking.\\
        \textbf{Languages:} Primarily \acr{C} \& \acr{C++}; \acr{Pascal}; \acr{C\#}; \acr{PHP}; Shell
        Scripting; \acr{SQL \& PL/SQL}.\\
    }}
}

\headedsection
  {\href{http://www.cenatav.co.cu}{CENATAV}}
  {\textsc{Havana, Cuba}} {%
  \headedsubsection
    {Lead Developer \& Researcher}
    {\apo08 -- \apo09}
    {\bodytext{
        \begin{itemize}
        \item Worked as a software developer on biometric solutions.
        \item Did a lot of reasearch as a PhD student on biometrics and specially on indexing of large
          fingerprint databases.
        \end{itemize}

        \vspace{1mm}

        \textbf{Skillset:} Operating Systems; Data Structures; Algorithms; Performance design and analysis;
        Biometrics; Networking.\\
        \textbf{Languages:} Primarily \acr{C} \& \acr{C++}; Shell Scripting; \acr{SQL}.\\
    }}
}

\vspace{-0.2em}
\begin{center}
  \emph{\small Please refer to \href{http://www.linkedin.com/in/jvillasante}{my LinkedIn profile} for a more complete list of work experiences along with recommendations.}
\end{center}


\spacedhrule{-0.2em}{-0.4em}

\roottitle{Education}

\headedsection
  {\href{http://cujae.edu.cu}{Instituto Superior Polit\'ecnico Jos\'e Antonio Echeverr\'ia} \textnormal{~(\acr{CUJAE})}}
  {\textsc{Havana, Cuba}} {%
  \headedsubsection
    {Bachelor degree in Computer Science \textnormal{~(\acr{CS})}}
    {2003 -- 2008}
    {\bodytext{Main courses in Programming Languages, Algorithms, Data Structures, Software Design, Software Architecture, Systems Engineering, C/C++, Web Technologies. Picked up quite some PHP and Java skills along the way.}}
}

\spacedhrule{0.5em}{-0.4em}

\roottitle{Skills}

\inlineheadsection  % special section that has an inline header with a 'hanging' paragraph
  {Technical expertise:}
  {Big fan of Agile methodologies and continuous delivery and functional programming. Enjoys writing C/\nsp\CPP\nsp\ mostly but has experience in other languages as well. Solid knowledge of SQL and relational databases (PostgreSQL, MySQL, SQLite). Solid knowledge of web technologies. Strong Linux administration skills (e.g.\ Bash scripting). Strong Embedded systems development and integration skills. Complex problem solver skills. Strong decision maker. Excellent communicator. Independent, organized, punctual, positive attitude, team player, fast learner. Happy Git user. Emacs and \acr{VIM} user.}

\vspace{0.5em}
\inlineheadsection
  {Natural languages:}
  {Spanish \emph{(mother tongue)}, English \emph{(full professional proficiency)}.}

\spacedhrule{1.6em}{-0.4em}

\roottitle{Interests}

\inlineheadsection
  {Non-exhaustive and in no apparent order:}
  {Internet of Things, Game Development, C++ future, Rust, Lisp, Artificial Intelligence, Functional Programming, Concurrency, Parallelism, Algorithms, Coding, Readable Code, Problem Solving, Linux/Unix Kernel, Embedded Development, New Technologies, Frameworks and Libraries, Software Architecture, TDD, Design Patterns, Software Design, Cryptography, Open Source, Startups.}

\end{document}
