% LaTeX source of my resume
% =========================

% Commented for easy reuse... ;)

% See the `README.md` file for more info.

% This file is licensed under the CC-NC-ND Creative Commons license.


% Start a document with the here given default font size and paper size.
\documentclass[10pt,a4paper]{article}

% Set the page margins.
\usepackage[a4paper,margin=0.75in]{geometry}

% For spanish accents and the like
\usepackage[utf8]{inputenc}

% Setup the language.
\usepackage[english]{babel}
\hyphenation{Some-long-word}

% Makes resume-specific commands available.
\usepackage{resume}


\begin{document}  % begin the content of the document
\sloppy  % this to relax whitespacing in favour of straight margins


% title on top of the document
\maintitle{Julio C. Villasante G\'omez}{May 24, 1980}{Last update on \today}

\nobreakvspace{0.3em}  % add some page break averse vertical spacing

% \noindent prevents paragraph's first lines from indenting
% \mbox is used to obfuscate the email address
% \sbull is a spaced bullet
% \href well..
% \\ breaks the line into a new paragraph
\noindent\href{mailto:jvillasantegomez.at.gmail.dot.com}{jvillasantegomez\mbox{}@\mbox{}gmail.com}\sbull
\textsmaller{+}1-786-282-1636\sbull
\href{https://github.com/jvillasante}{github.com/jvillasante}\sbull
\href{http://linkedin.com/in/jvillasante}{linkedin.com/in/jvillasante}
\\
8405 Northwest 8{\large \sc th} Street {\large \sc Apt.}\thinspace 406\sbull
Miami,\thinspace FL\sbull
{\large \sc 33126}\sbull
USA

\spacedhrule{0.9em}{-0.4em}  % a horizontal line with some vertical spacing before and after

\roottitle{Summary}  % a root section title

\vspace{-1.3em}  % some vertical spacing
\begin{multicols}{2}  % open a multicolumn environment
\noindent \emph{Savvy Software Developer with 7+ years in technical software development. Expert in a variety of platforms, languages and embedded systems.}
\\
\\
An excellent problem solver, able to quickly grasp complex systems and identify opportunities for improvements and resolution of critical issues.

Have interest in designing and crafting efficient modern software, and learning new technologies and tools if need arises.
\end{multicols}

\spacedhrule{0em}{-0.4em}

\roottitle{Experience}

\headedsection {\textsc{Node.js}} {
    \begin{itemize}
      \item express.js
      \item Persistence with mongodb (mongoskin, mongoose), redis, and
        relational databases (MySQL, PostgreSQL)
      \item passport.js to authorize and authenticate users in Node.js apps
      \item async, lodash, crypto, http, ArrayBuffers, Streams, stdio, child
        processes, etc \ldots
      \item TDD and BDD for Node.js with Mocha
      \item Modular design and development
      \item Template engines (jade and handlebars)
      \item Real-Time apps with WebSocket, Socket.io
      \item Deploying and production maintenance of Node.js apps
    \end{itemize}
}

\headedsection {\textsc{Frontend}} {
    \begin{itemize}
      \item Javascript, jQuery
      \item Angular.js
      \item React.js / Flux
      \item HTML5, CSS3, LESS
      \item Twitter Bootstrap, UX/UI Design
    \end{itemize}
}

\headedsection {\textsc{Server}} {
    \begin{itemize}
      \item Linux (Debian and Ubuntu), SSH shell, Load Balancing
      \item Apache, nginx, SSL certificates
      \item Git repositories
      \item Server deployment (AWS, pm2)
      \item Mongodb, redis, MySQL, PostgreSQL
      \item Shell scripting
    \end{itemize}
}

\headedsection {\textsc{Software}} {
    \begin{itemize}
      \item Emacs, Vim
      \item Visual Studio, QtCreator, eclipse
      \item C/C++, gcc, make
    \end{itemize}
}

\roottitle{Employment History}

\headedsection
  {\href{http://innobis.cl}{Innobis}}
  {\textsc{Santiago, Chile}} {%
  \headedsubsection
    {Lead Developer}
    {Jan \apo15 -- June \apo15}
    {\bodytext{
      Innobis is an open source minded ``full-service'' internet company based
      in Santiago, Chile which fuels innovation from conception to deployment of
      software solutions.
      \\
      \\
      {Responsibilities:}
      \begin{itemize}
        \item Plan and Manage team goals in implementing new technologies and features
        \item RESTful API development and documentation
        \item Single page application design and development using React.js and Flux
        \item Analytical and geolocation tracking on click traffic, and real
          time graphical presentation
        \item High traffic load balancing and distribution
        \item Got everyone to look beyond PHP to other open source solucions
          such as Node.js
        \item Helped to set up customer support
        \item On call support for all problems that may arise
        \item Contributed to the sales pitches and in charge of the software
          architecture off all technically challenging projects.
      \end{itemize}
    }}
}

\headedsection
  {\href{http://www.genera.cl}{Genera S.A.}}
  {\textsc{Santiago, Chile}} {%
  \headedsubsection
    {Lead Developer \& Researcher}
    {Jan \apo14 -- Jan \apo15}
    {\bodytext{
      Genera S. A. is a Human Resources Management company which uses advanced
      technology to better manage the human factor on their clients.
      \\
      \\
      {Responsibilities:}
      \begin{itemize}
        \item C/C++ and QT development and maintenance
        \item Research and development of biometric (fingerprint identification)
          solutions
        \item RESTful API conception and development on servers for the
          different biometric clients
        \item Fingerprint image manipulation and processing
        \item Linux development and installation/configuration on ARM boards
        \item Worked closely with sensors and other kinds of hardware on our
          embedded systems
        \item On call support for all problems that may arise
      \end{itemize}
    }}
}

\headedsection
  {\href{http://www.datys.cu}{Datys}}
  {\textsc{Havana, Cuba}} {%
  \headedsubsection
    {Lead Developer}
    {\apo09 -- Jan \apo14}
    {\bodytext{
      Datys is a Cuban company which has made great strides on the last few
      years both on Cuba as in Latin America.
      \\
      \\
      {Responsibilities:}
      \begin{itemize}
        \item Conception and development of software solutions af all kinds
        \item PHP and Javascript development of different web clients
        \item RESTful API interface to open the backend domain to the different
          clients
        \item Embedded system programming for POS software
        \item Lots of SQL (Oracle) development and maintenance
        \item Integration, monitoring and maintenance of different modules and applications
      \end{itemize}
    }}
}

\vspace{-0.2em}
\begin{center}
  \emph{\small Please refer to \href{http://www.linkedin.com/in/jvillasante}{my LinkedIn profile} for a more complete list of work experiences along with recommendations.}
\end{center}


\spacedhrule{-0.2em}{-0.4em}

\roottitle{Education}

\headedsection
  {\href{http://cujae.edu.cu}{Instituto Superior Polit\'ecnico Jos\'e Antonio Echeverr\'ia} \textnormal{~(\acr{CUJAE})}}
  {\textsc{Havana, Cuba}} {%
  \headedsubsection
    {Bachelor degree in Computer Science \textnormal{~(\acr{CS})}}
    {2003 -- 2008}
    {\bodytext{Main courses in Programming Languages, Algorithms, Data
        Structures, Software Design, Software Architecture, Systems Engineering,
        C/C++, Web Technologies. Picked up quite some PHP and Java skills along
        the way.}}
}

\spacedhrule{0.5em}{-0.4em}

\roottitle{Skills}

\inlineheadsection  % special section that has an inline header with a 'hanging' paragraph
  {Technical expertise:}
  {Big fan of Agile methodologies and continuous delivery and functional
    programming. Enjoys writing C/\nsp \CPP/\nsp Go/\nsp PHP/\nsp Java~and
    JavaSript. Solid knowledge of SQL and relational databases (PostgreSQL,
    MySQL, Oracle, SQLite). Solid knowledge of web technologies. Able to
    architect and implement distributed systems. Strong Linux administration
    skills (e.g.\ Bash scripting). Strong Embedded systems development and
    integration skills. Complex problem solver skills. Strong decision maker.
    Excellent communicator. Independent, organized, punctual, positive attitude,
    team player, fast learner. Git, Emacs and \acr{VIM} user.}

\vspace{0.5em}
\inlineheadsection
  {Natural languages:}
  {Spanish \emph{(mother tongue)}, English \emph{(full professional proficiency)}.}


\spacedhrule{1.6em}{-0.4em}

\roottitle{Interests}

\inlineheadsection
  {Non-exhaustive and in no apparent order:}
  {Internet of Things (IoT), Mobile Development, Cloud Computing, Big Data,
    Functional Programming, Concurrency, Algorithms, Coding, Readable Code,
    Problem Solving, Linux/Unix Kernel, Embedded Development, New Technologies,
    Frameworks and Libraries, Web Development, Software Architecture, NoSQL,
    TDD, Design Patterns, Software Design, Cryptography, Open Source, Startups.}

\end{document}
